Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-04 PAPER.tex
did a comb through of the first half of the paper for typos/syntax

One promising technique to probe the EoR is to target the 21 cm wavelength emission that is emitted and absorbed by neutral hydrogen via 
its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}); . This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
stretching out as it traveled through expanding space. Tracing the 21 cm line as a function of redshift offers a window into the 
evolution of ionization, temperature, and density fluctuations during this transformative era.

@@

The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires

an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
the accuracy and reliability of a potential EoR detection. In this paper, we discuss three themes that are essential to investigate 
for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 $21$ cm power spectrum 
from the lessons learned.

This paper is organized into two main sections. In Section \ref{sec:Themes} we introduce the three themes of our focus, using a 
toy model to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015}, henceforth known as P64, which have led to a 
revised PAPER-64 power spectrum result (Kolopanis et al., \textit{in prep}). We conclude in Section \ref{sec:Con}.

@@

There are many choices a data analyst must consider. How can time-ordered measurements be combined? How can the 
variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
destroying an EoR signal? How can the source of a detection be properly identified? Many common techniques, such as 
averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
some EoR signal. A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.

@@

A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power 
spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for 
a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target cosmological signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of positive power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for $21$ cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}

@@

The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in 
data. However, some have limitations, and we will discuss circumstances in which there are trade-offs. We choose to focus on 
these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also 
being standard steps in general $21$ cm analyses.
\begin{itemize}
\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data 
(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of 
independent samples by an amount dependent on the width of the averaging window. However, it can also affect the presence 
of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others. One particular flavor of 
weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}). This weighting has the effect of down-weighting correlated 
information (i.e. foregrounds) and up-weighting noise-like information (i.e. EoR). However, a challenge of inverse covariance 
weighting is in accurately defining a covariance matrix that best describes the data. 
\item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
methods, bootstrapping is one way to estimate errors. Bootstrapping is a useful method for estimating errors of a dataset from 
itself (\citealt{andrae2010}). By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
consider such as the independence of values in a dataset.
\item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different 
dimensions of a dataset to cross-validate results. In particular, null tests can be used to verify whether results are free of 
systematics, as done with CO power spectra (\citealt{keating_et_al2016}) and CMB measurements (see e.g. \citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}). An EoR detection must pass jack-knife and null tests.
\end{itemize}

@@

We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy. It has length ($N_{t}, N_{f}$), where 
$N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
the Fourier transform of the sky along $2$ spatial dimensions (using the flat-sky approximation), and since we are interested in $3$-dimensional Fourier-modes 
we only need to take one Fourier transform of our data along the line-of-sight dimension. We do this when forming the un-
normalized power spectrum estimate $\hat{q}_{\alpha}$:

\begin{equation}
\label{eq:qhat}
\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}.
\end{equation}

\noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier-transforms them into 
power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to 
Kelvin, as well as cosmological scalings. The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the 
Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}). $\textbf{R}$ is a weighting matrix --- as 
an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $
\textbf{R} = \textbf{I}$, the identity matrix.

@@

In the next three sections, we investigate the effects of weighting matrices on signal loss by experimenting with different 
matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$. Our ultimate goal in 
experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections, for 
the sake of completeness. The specifics of how signal loss appears in PAPER's analysis is later described in Section 
\ref{sec:Sigloss}.

@@

To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss, we 
use a toy model. We construct a simple dataset that contains 2-dimensional data (representing visibility data with $100$ time 
integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
might be used for a power spectrum analysis. For PAPER-64 (both the previous analysis and our new analysis)we use $\sim$eight hours of data for our analysis (with channel 
widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of 
generality.

We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift scan observation. Hence, flat spectrum sources (away 
from zenith) oscillate in time and frequency in our measurements. We therefore form a mock bright foreground signal, $
\textbf{x}_{FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a 
single bright source. We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal. A more 
realistic EoR signal would have a sloped power spectrum in $\textbf{p}$(k) (instead of flat, as in the case of white noise), 
which could be simulated by introducing frequency correlations into the mock EoR signal. However, in this paper we treat all 
$k$'s separately, so a simplistic white noise approximation can be used. Our combined data vector is then $\textbf{x} = 
\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes. The three data vectors are shown in Figure 
\ref{fig:toy_sigloss1}.

@@

Therefore, one attractive way to estimate $\textbf{C}$ is to empirically derive it from the data vector $\textbf{x}$ itself:

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). The foregrounds peak at a $k$ mode based on the frequency of the sinusoid used to create it. We compare inverse covariance weighting 
where $\textbf{C}$ is derived from the data (left), with projecting out the first eigenmode only (right). In the former 
case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
empirically estimated, its eigenvalues pose the risk of describing random fluctuations that happen to exist in the data realization 
but may not exist in the true covariance. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
which $\hat{\textbf{C}}$ does not describe accurately.}
	\label{fig:toy_sigloss3}
\end{figure*}

As shown, our inverse covariance-weighted result successfully suppresses foregrounds. It is also evident that our result fails to 
recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low. This is evidence of signal loss. In 
order to understand the behavior of this result, we can closely study our covariance matrix, $\hat{\textbf{C}}$. %, which is 
shown in Figure \ref{fig:toy_sigloss12}.

If $\textbf{C}$ is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a 
multiplicative bias (per $k$) to estimates of the signal. For a mathematical derivation of signal loss arising from a data-
estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}. Here we will describe the origin of this signal loss 
intuitively.

@@

If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue and eigenvector of $\textbf{C}$ would be 
representative of real fluctuations in the data. However, when using an estimated $\hat{\textbf{C}}$ that is derived from one 
particular data realization, its eigenvalues and eigevectors may differ from the truth. Said differently, shapes that may not exist (or have a 
weaker existence) in a true covariance may appear stronger in the estimated covariance. Hence, they will be down-weighted 
more than they should be.

In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are expected to be dominated by bright foregrounds 
--- the most prominent shapes in the data. For these `strong' modes, where foregrounds outshine the EoR signal, $
\hat{\textbf{C}} \sim \textbf{C}$ and down-weighting these modes is beneficial. This is demonstrated in the toy model by the 
successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and 
assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}). In Figure \ref{fig:toy_sigloss12} we show the 
covariances of our toy model datasets along with inverse covariance weighted data. The foreground sinusoid is clearly visible in 
$\hat{\textbf{C}}_{FG}$ but effectively absent from $\hat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.

@@

The danger of an empirically estimated covariance matrix comes from not being able to describe the `weak' eigenmodes of $
\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds. If these weak eigenmodes of $\hat{\textbf{C}}$ 
characterize EoR modes, the EoR signal will be down-weighted (not as much as the strong foreground modes, but still down-
weighted). This leads to the `overfitting' of noise (or `overfitting' of signal), which is signal loss.

Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield zero 
signal loss. Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode. We can 
project out the zeroth eigenmode (i.e. zero out all eigenmodes except the first one), thereby down-weighting the foreground-dominating mode only. Hence, we are not using information from all the weaker eigenmodes which carry the risk of 
describing EoR fluctuations. Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are 
changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover EoR, 
demonstrating that if we can disentangle the foreground-dominating modes from EoR-dominating modes, we can down-weight 
them without signal loss. There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section 
\ref{sec:otherweight}.

\subsubsection{Toy Model: Fringe-Rate Filtering}

@@

The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
\ref{fig:toy_sigloss5} (right plot). The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data. With 
fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
true covariance matrix. In some cases one might even arrive at a rank-deficient empirical covariance, which is unphysical given 
that instrumental noise makes it impossible for any mode to truly have zero variance. \acl{Was there noise in this figure? Also, I 
am slightly uncomfortable with the figure. FRF \emph{should} affect the covariance, since the data is different. What would 
really tease out the difference between the covariance matrix simply being different vs. us not being able to estimate the 
covariance matrix would be if we ran a large ensemble of these, and we saw the empirical covariance converging to something. 
Can we make such a figure?} The situation is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
of the matter power spectrum is estimated using a large---but finite---number of expensive simulations. There, the limited 
number of independent simulations results in inaccuracies in estimated covariance matrices 
\citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints 
\citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
as we argue in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}, the resulting estimates are biased 
\emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ 
cosmology. These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of 
theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, 
marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods 
\citep{pope_szapudi2008,joachimi_2017}.

@@

In summary, we have a choice of how to weight $21$ cm data. Ideally, we want to down-weight bright foregrounds without 
removing the underlying cosmological signal. As we investigated however, there are trade-offs between the weighting method 
used, its foreground-removal effectiveness, and the amount of resulting signal loss.

>>>>

One promising technique to probe the EoR is to target the 21 cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}); . This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
stretching out as it traveled through expanding space. Tracing the 21 cm line as a function of redshift offers a window into the 
evolution of ionization, temperature, and density fluctuations during this transformative era.

@@

The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
the accuracy and reliability of a potential EoR detection. In this paper, we discuss three themes that are essential to investigate 
for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
from the lessons learned.

This paper is organized into two main sections. In Section \ref{sec:Themes} we introduce the three themes of our focus, using a 
toy model to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as P64, which have led to a 
revised PAPER-64 power spectrum result (Kolopanis et al., \textit{in prep}). We conclude in Section \ref{sec:Con}.

@@

There are many choices a $21$ cm data analyst must consider. How can time-ordered measurements be combined? How can the 
variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
destroying an EoR signal? How can the source of a detection be properly identified? Many common techniques, such as 
averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
some EoR signal. A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.

@@

A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power 
spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for 
a rigorous power spectrum analysis.
\begin{itemize}
\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target cosmological signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result. 
\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a $21$ cm power spectrum result 
determine the difference between a detection and a null result, which have two very different implications. Errors can be 
estimated in a variety of ways, and we will discuss a few of them.
\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of positive power offset in a visibility 
measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for $21$ cm 
analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
pass.
\end{itemize}

@@

The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in 
data. However, some have limitations, and we will discuss circumstances in which there are trade-offs. We choose to focus on 
these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also 
being standard steps in general $21$ cm analyses.
\begin{itemize}
\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data 
(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of 
independent samples by an amount dependent on the width of the averaging window. However, it can also affect the presence 
of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.
\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others. One particular flavor of 
weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}). This weighting has the effect of down-weighting correlated 
information (i.e. foregrounds) and up-weighting noise-like information (i.e. EoR). However, a challenge of inverse covariance 
weighting is in accurately defining a covariance matrix that best describes the data. We investigate the impact of different types of weighting on signal loss in Section \ref{sec:SiglossOverview}.
\item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
methods, bootstrapping is one way to estimate errors. Bootstrapping is a useful method for estimating errors of a dataset from 
itself (\citealt{andrae2010}). By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
consider such as the independence of values in a dataset. We explore potential pitfalls of bootstrapping in Section \ref{sec:ErrorOverview}.
\item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different 
dimensions of a dataset to cross-validate results. In particular, null tests can be used to verify whether results are free of 
systematics, as done with CO power spectra (\citealt{keating_et_al2016}) and CMB measurements (see e.g. \citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}). An EoR detection must pass jackknife and null tests, which we highlight in Section \ref{sec:JackknifeOverview}.
\end{itemize}

@@

We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy. It has length ($N_{t}, N_{f}$), where 
$N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
the Fourier transform of the sky along $2$ spatial dimensions (using the flat-sky approximation), and since we are interested in $3$-dimensional Fourier-modes 
we only need to take one Fourier transform of our visibilities along the line-of-sight dimension. We do this when forming the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:

\begin{equation}
\label{eq:qhat}
\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}.
\end{equation}
Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier-transforms them into 
power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to 
Kelvin, as well as cosmological scalings. The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the 
Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}). $\textbf{R}$ is a weighting matrix --- as 
an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $
\textbf{R} = \textbf{I}$, the identity matrix.

@@

In the next three sections, we investigate the effects of weighting matrices on signal loss by experimenting with different 
matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$. Our goal in 
experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections. The specifics of how signal loss appears in PAPER's analysis is later described in Section 
\ref{sec:Sigloss}.

@@

To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss, we 
use a toy model. We construct a simple dataset that contains 2-dimensional data (representing visibility data with $100$ time 
integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
might be used for a power spectrum analysis. For PAPER-64 (both the previous analysis and our new analysis) we use $\sim$$8$ hours of data for our analysis (with channel 
widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of 
generality.

We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift scan observation. Hence, flat spectrum sources (away 
from zenith) oscillate in time and frequency in our measurements. We therefore form a mock bright foreground signal, $
\textbf{x}_{FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a 
single bright source. We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal. A more 
realistic EoR signal would have a sloped power spectrum in $\textbf{p}$(k) (instead of flat, as in the case of white noise), 
which could be simulated by introducing frequency correlations into the mock EoR signal. However, in this paper we treat all 
$k$'s separately, so a simplistic white noise approximation can be used. Our combined data matrix is then $\textbf{x} = 
\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes. The three data matrices are shown in Figure 
\ref{fig:toy_sigloss1}.

@@

Therefore, one attractive way to estimate $\textbf{C}$ is to empirically derive it from the data $\textbf{x}$ itself:

@@

\begin{figure*}
	\centering
	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). The power spectrum of foregrounds peaks at a $k$ mode based on the frequency of the sinusoid used to create the mock FG signal. In the two panels, we compare inverse covariance weighting 
where $\textbf{C}$ is derived from the data (left),and projecting out the first eigenmode only (right). In the former 
case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
empirically estimated, its eigenvalues pose the risk of describing EoR-dominating modes. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
which $\hat{\textbf{C}}$ does not describe accurately.}
	\label{fig:toy_sigloss3}
\end{figure*}

As shown, our inverse covariance-weighted result successfully suppresses foregrounds. It is also evident that our result fails to 
recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low. This is evidence of signal loss. In 
order to understand the behavior of this result, we can closely study our covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
%, which is shown in Figure \ref{fig:toy_sigloss12}.

If $\textbf{C}$ is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a 
multiplicative bias (per $k$) to estimates of the signal. For a mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}. Here we will describe the origin of this signal loss 
intuitively.

@@

If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue and eigenvector of $\textbf{C}$ would be 
representative of real fluctuations in the data. However, when using an estimated $\hat{\textbf{C}}$ that is derived from one 
particular data realization, its eigenvalues and eigenvectors may differ from the truth. Said differently, shapes that may not exist (or have a 
weaker existence) in a true covariance may appear stronger in the estimated covariance. Hence, they will be down-weighted 
more than they should be.

In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are expected to be dominated by bright foregrounds 
--- the most prominent shapes in the data. For these `strong' modes, where foregrounds outshine the EoR signal, $
\hat{\textbf{C}} \sim \textbf{C}$ and down-weighting these modes is beneficial. This is demonstrated in the toy model by the 
successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and 
assigns it the highest eigenvalue (the first peak in Figure \ref{fig:toy_sigloss2}). In Figure \ref{fig:toy_sigloss12} we show the 
covariances of our toy model datasets along with inverse covariance weighted data. The foreground sinusoid is clearly visible in 
$\hat{\textbf{C}}_{FG}$ but effectively absent from $\hat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.

@@

The danger of an empirically estimated covariance matrix comes from not being able to describe the `weak' eigenmodes of $
\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds. If these weak eigenmodes of $\hat{\textbf{C}}$ 
characterize EoR modes, the EoR signal will be down-weighted (not as much as the strong foreground modes, but still down-weighted). This leads to the `overfitting' of noise (or rather `overfitting' of signal), which is signal loss.

Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield minimal 
signal loss. Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode. We can 
project out the zeroth eigenmode (i.e. zero out all eigenmodes except the first one), thereby down-weighting the foreground-dominating mode only. Hence, we are not using information from all the weaker eigenmodes which carry the risk of 
describing EoR fluctuations. Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are 
changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover EoR, 
demonstrating that if we can disentangle the foreground-dominating modes from EoR-dominating modes, we can down-weight 
them without signal loss. There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section 
\ref{sec:otherweight}.

\subsubsection{Toy Model: Fringe-Rate Filtering}
\label{sec:toymodel_frf}

@@

The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
\ref{fig:toy_sigloss5} (right plot). The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data. With 
fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
true covariance matrix. In some cases one might even arrive at a rank-deficient empirical covariance, which is unphysical given 
that instrumental noise makes it impossible for any mode to truly have zero variance. \acl{Was there noise in this figure? Also, I 
am slightly uncomfortable with the figure. FRF \emph{should} affect the covariance, since the data is different. What would 
really tease out the difference between the covariance matrix simply being different vs. us not being able to estimate the 
covariance matrix would be if we ran a large ensemble of these, and we saw the empirical covariance converging to something. 
Can we make such a figure?} The situation is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
of the matter power spectrum is estimated using a large --- but finite --- number of expensive simulations. There, the limited 
number of independent simulations results in inaccuracies in estimated covariance matrices 
\citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints 
\citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
as we argue in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}, the resulting estimates are biased 
\emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ 
cosmology. These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of 
theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, 
marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods 
\citep{pope_szapudi2008,joachimi_2017}.

@@

In summary, we have a choice of how to weight $21$ cm data. Ideally, we want to down-weight bright foregrounds without 
removing the underlying cosmological signal. As we investigated however, there are trade-offs between the weighting method 
used, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
